
```{r, setup, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  tidy = FALSE,
  error = FALSE,
  fig.width = 8,
  fig.height = 8)
```

# pkgsnap

> Backup and Restore Certain CRAN Package Versions

[![Linux Build Status](https://travis-ci.org/MangoTheCat/pkgsnap.svg?branch=master)](https://travis-ci.org/MangoTheCat/pkgsnap)
[![Windows Build status](https://ci.appveyor.com/api/projects/status/github/MangoTheCat/pkgsnap?svg=true)](https://ci.appveyor.com/project/gaborcsardi/pkgsnap)
[![Coverage Status](https://img.shields.io/codecov/c/github/mangothecat/pkgsnap/master.svg)](https://codecov.io/github/mangothecat/pkgsnap?branch=master)
[![](http://www.r-pkg.org/badges/version/pkgsnap)](http://www.r-pkg.org/pkg/pkgsnap)
[![CRAN RStudio mirror downloads](http://cranlogs.r-pkg.org/badges/pkgsnap)](http://www.r-pkg.org/pkg/pkgsnap)


Create a snapshot of your installed CRAN packages with 'snap', and then
use 'restore' on another system to recreate exactly the same environment.

## Installation

```{r eval = FALSE}
devtools::install_github("mangothecat/pkgsnap")
```

## Usage

```{r}
library(pkgsnap)
```

For this experiment we create a new library directory, and install
some packages there. We will then remove this directory entirely,
and recreate it using `pkgsnap`.

```{r}
lib_dir <- tempfile()
dir.create(lib_dir)
```

We make this new library directory the default:

```{r}
.libPaths(lib_dir)
```

The new library directory is currently empty:

```{r}
installed.packages(lib_dir)[, c("Package", "Version")]
```

Let's install some packages here. Note that the dependencies of these
packages will be also installed.

```{r}
install.packages(c("testthat", "pkgconfig"))
installed.packages(lib_dir)[, c("Package", "Version")]
```

We will now create a snapshot, and then scrap the temporary package
library.

```{r}
snapshot <- tempfile()
snap(to = snapshot)
read.csv(snapshot)[1:5,]
unlink(lib_dir, recursive = TRUE)
```

Create a new package library.

```{r}
new_lib_dir <- tempfile()
dir.create(new_lib_dir)
.libPaths(new_lib_dir)
```

Finally, recreate the same set of package versions, in a new package
library.

```{r}
restore(snapshot)
installed.packages(new_lib_dir)[, c("Package", "Version")]
```


## License

MIT © [Mango Solutions](https://github.com/mangothecat).
